Automatic line-by-line semi-empirical models for high-grasp stellar and telluric spectra

### 2022-08-10 paper/paper1/ms.tex
The paper is beginning to look near complete, yay

\subsection{Accretion Veiling}

@@

>>>>

\subsection{Accretion Veiling}
To-be-completed

@@

Blas\'e already performs very well under a wide range of cloning and transfer-learning tasks.  However, some precision applications may demand even-more-strenuous performance than what the current implementation can accomodate.  Here we describe some of these technical improvements, their design, and/or mention some science case they may unlock.
